---
title: "xpower2dist"
author: "Dennis Mandere"
date: "4/11/2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Xpower2dist
Is a package that enables a user to calculate the expected cell frequencies in a chi square test of independence.
For the test to work the following conditions must be met:
*The expected cell values must be >5.
*The sample size must be large enough.
*Two categorical variables.
*Two or more categories for each variable.
*The observations must be independent of each other.

T
```{r}
Jay = function(x) {
  x = observed_table<-matrix(c(32,30,28,74,64,42,110,25,15,39,6,5),
                             nrow = 4,ncol = 3,byrow = T)
  row.names(observed_table) <-c('Dormitory','On_campus','Off_campus','At home')
  colnames(observed_table) <-c('No_regular','Sporadic','Regular')
  chis <- chisq.test(observed_table)
  y = round(chis$expected,2)
  return(y)
}

```

##
# FAQ of Xpower2dist
#Q:What is xpower2dist
#A:It is a package that enables users to get the expected cell frequency values
#in a chi square test of independence.
#Q:What are the functions that this package depends on?
#A:It depends on the chisq.test function
#Q:What type of data set is deployed?
#A:The data can be a vector,matrix,data frame,table
#NB
#This is work on progress more details and functions will be added
