
 ---
title: "xpowergood"
author: "Dennis Mandere"
date: "4/26/2022"
output: html_document
---
***Xpowergood package***

**Introduction**
This is a package that returns the expected cell frequencies in a chi square 
test of independence.The expected cell frequencies formula is:
Expected cell frequency=(Row total*column total)/N.

This is then used in the chi square test of independence.The test statistic is:
(observed cell frequencies-Expected cell frequencies)^2/Expected cell frequencies
(O-E)^2/E

For this package to work the sample observations are independent of each other and the sample size is large enough(expected cell frequency of each cell n>5) for at least two categorical variables or more.
inside groups for each variable.
```{r}
library(xpowergood)

```

The following functions are applicable to this package

**Jael function**

```{r showandtell,results='markup',eval=TRUE}
jael<-function(x) {
  x = observed_table<-matrix(c(34,30,28,74,62,42,110,25,15,39,8,7),
                             nrow = 4,ncol = 3,byrow = T)
  row.names(observed_table) <-c('Dormitory','On_campus','Off_campus','At home')
  colnames(observed_table) <-c('No_regular','Sporadic','Regular')
  chis <- chisq.test(observed_table)
  y = round(chis$expected,2)
  return(y)
}
```



##
**mos function**

Returns a mosaic plot of the contigency table which shows the frequencies of the
observations
```{r}
mos<-function(h) {
  h = mosaicplot(observed_table,main = "Exercise by living arrangemet",
                 ylab = "Exercise status",
                 xlab = "residence",col = c(2,3,4))
}
```

**bay function**
Returns a bar plot of the exercise status and the living arrangement.

```{r}
bay<-function(k)  {
  k = barplot(observed_table,ylab="Residence", xlab="Exercise status",
              main="Exercise by living arrangement",
              col = c("turquoise4","turquoise3","turquoise2", "turquoise"),
              beside = T, width = .3)
}
```

***Resources***

Essentials of Biostatistics in public health, Third edition. Lisa M. Sullivan

